The Transition from Massive Metal Free Stars to Dwarf Galaxies

### 2011-01-26 ms.tex
Adding some text for Pop III enrichment section.

\begin{figure*}
  \epsscale{2}
  \plotone{bmosaic.eps}
  \epsscale{1}
  \caption{\label{fig:evo-mosaic} Evolution of the entire simulation
    volume at redshifts 15, 12, 10, 8, and 7 (left to right).
    Pictured here are the density-weighted projections of density
    (top), temperature (middle), and metallicity (bottom).  Note how
    the stellar radiative feedback from low-mass galaxies reionize
    the majority of the volume.  The metallicity projections are a
    composite image of metals originating from Pop II (blue) and III
    (red) stars with magneta indicdating a mixture of the two.}
\end{figure*}

@@

Given the idea of most minihaloes host a Pop III, these numbers appear
low.  However there are a few processes that can suppress Pop III star
formation:
%
\begin{enumerate}
\item photo-dissociation of \hh~\citep{Dekel87, Haiman00, Machacek01},
\item photo-evaporation of minihaloes \citep{Shapiro04, whalen08}, and
\item metal enrichment from nearby (PI)SNe \citep{Wise08_Gal, Greif10,
  Trenti09}.
\end{enumerate}
We observe all of these affecting Pop III star formation in the
simulation, confirming that negative feedback plays an important role
in metal-free star formation.

@@

@@

\subsubsection{Gas fraction evolution}

>>>>

\begin{figure*}
  \epsscale{2}
  \plotone{bmosaic.eps}
  \epsscale{1}
  \caption{\label{fig:evo-mosaic} Evolution of the entire simulation
    volume ($L_{\rm box} = 1$ Mpc) at redshifts 15, 12, 10, 8, and 7
    (left to right).  Pictured here are the density-weighted
    projections of density (top), temperature (middle), and
    metallicity (bottom).  Note how the stellar radiative feedback
    from low-mass galaxies reionize the majority of the volume.  The
    metallicity projections are a composite image of metals
    originating from Pop II (blue) and III (red) stars with magneta
    indicdating a mixture of the two.}
\end{figure*}

@@

Given the idea of most minihaloes host a Pop III, these numbers appear
low.  However there are a few processes that can suppress Pop III star
formation:
%
\begin{enumerate}
\item photo-dissociation of \hh~\citep{Dekel87, Haiman00, Machacek01},
\item photo-evaporation of minihaloes \citep{Shapiro04, whalen08}, and
\item metal enrichment from intrinsic and nearby (pair-instability)
  SNe \citep{Wise08_Gal, Trenti09, Greif10}.
\end{enumerate}
We observe all of these affecting Pop III star formation in the
simulation, confirming that negative feedback plays an important role
in metal-free star formation.

@@

We plot the evolution of the mass-averaged gas and stellar metallicity
in the massive halos in Fig. \ref{fig:Zevo}.  Here we focus on the
metallicity provided from Pop III SNe, \zthree.  The most relevant
aspect of these data is the existence of a metallicity floor $\zthree
\sim -3$ in all of the haloes.  The haloes can either be enriched from
hosting a PISNe or one in a nearby halo.  In the time evolution of the
metallicity, the former scenario appears as an initial peak in
\zthree~then gradually decreasing, which is seen in Haloes 1-3 and 6-9
with two enrichment events occurring in Halo 6.  This peak happens
because the halo is gas-poor from the Pop III radiative feedback with
$M_{\rm gas} \sim 10^4$ (also see Sec. \ref{sec:fgas}) and the PISN
provides $\sim 100 \Ms$ of heavy elements, resulting in $\zthree \sim
0$.  The ensuing blastwave drives out the remainder of the gas,
leaving behind a diffuse medium, enriched to $\zthree \ga -3$.
Because the blastwave rapidly exits the halo on timescales smaller
than the time sampling in Fig. \ref{fig:Zevo}, the maximum mean
metallicity is missed in most haloes but is captured in Halo 2.

Gas in satellite haloes and adjacent filaments are enriched to a
lesser extent because these high-density regions are resistant to
impinging metal-rich blastwaves \citep[cf.][]{Cen08}.  However if the
nearby SNe is close enough when the shock velocities are still high
($\ga 100~\kms$), the dense gas in the minihalo can be enriched to
similar metallicities.  This scenario appears as prompt enrichment but
without the temporary peak in metallicity as the blastwave overtakes
the halo, and this occurs in Haloes 0, 4, and 5 with Halo 5 being
enriched by two nearby PISNe.

In Figure \ref{fig:zhalo3}, we show the average \zthree~in all haloes
as a function of halo mass at $z =$ 7, 8, 9, and 10, and it is
strongly dependent on halo mass.  The \zthree~error bars mark the 25\%
and 75\% percentiles of the distribution at $M = M_{\rm halo}$ because
the underlying distribution is not necessarily Gaussian at all halo
masses.  Above $3 \times 10^7 \Ms$, all haloes enriched to $\zthree
\ga -4$ with little time evolution, further illustrating the
metallicity floor.  Below this halo mass, the distribution is roughly
bimodal composed of pristine and metal-enriched halos.

\li Add figure and describe metal filling fraction evolution.

@@

\subsubsection{Gas fraction evolution}
\label{sec:fgas}
